\Large \bf On semidefinite-representable sets over valuation fields

### 2025-05-23 article/paper_padic_spec.tex
commit by Simone

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs} 
\usepackage{graphicx}
\usepackage{color,xcolor}
\usepackage{ulem}
\usepackage{bm}

@@

In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. The main example is the field of $p$-adic numbers with $p$-adic valuation. Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving}.

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs} 
\usepackage{graphicx}
\usepackage{color,xcolor}
%\usepackage{ulem}
\usepackage{bm}

@@

In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. The main example is the field of $p$-adic numbers with $p$-adic valuation. Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.
